%% $RCSfile: proj_proposal.tex,v $
%% $Revision: 1.3 $
%% $Date: 2016/06/10 03:44:08 $
%% $Author: kevin $

\documentclass[11pt, a4paper, twoside, openright]{report}

\usepackage{float} % lets you have non-floating floats
\usepackage{url} % for typesetting URLs
\usepackage{wrapfig}
\usepackage[image,ecs]{vuwproject}

\renewcommand{\thesection}{\arabic{section}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}

%  We don't want figures to float so we define

\newfloat{fig}{thp}{lof}[chapter]
\floatname{fig}{Figure}
\graphicspath{ {./Figures/} }

 

\title{Work Experience Reflective Report}
\author{Niels Daniel Clayton}
\otherdegree{Honours of Electronic and Computer System Engineering}
\date{}
\begin{document}


\begin{summary}
    
    Over the summer of 2020-21 I worked as a research assistant at the Robinson Research facility. In this position I assisted a current PhD student to build a robotic data collection platform, and worked closely with a large group of professionals both at the facility and across New Zealand. This experience has helped me to develop and improve on a range of important professional skills that are invaluable to the progression of my degree.
    
    Through my time at the Robinson Research facility I was involved in both small scale, and large scale multi-company projects. From these projects I have learned that the key skill required to effectively contribute to a team are communication, and management of time, work, and others. I have found that these soft skills I have developed at this position are not only applicable to work, but also to my personal and university projects.   

\end{summary}

% Make the page numbering Roman, until after the contents, etc.
\frontmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\tableofcontents

\vfill

\section*{Acknowledgements}

I would like to acknowledge my supervisor Dr Fiona Stevens McFadden for the management and general advice she provided me with for the extent of this position. She made sure that I always felt comfortable in my work environment, and was always willing to give advice for any issues I encountered. She has also provided me with opportunities to work on a range of different projects over this time. I would also like to acknowledge the PhD student I was assisting in this time, Payam Nori Zadeh. He greatly encouraged me to expand my way of thinking and pushed me to learn new and helpful skills.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mainmatter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\section{Providing Context}

\section{Reflecting on the Experience}

\section{Conclusions}

\end{document}
